\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}




%by: Aline R. Antunes

\begin{document}
\begin{center}
    \textbf{Divyam Jani}\\ 
    \hrulefill
\end{center}

\begin{center}
    Morbi, Gujarat \textbullet \ divyamjani2004@gmail.com \textbullet \  \url{https://github.com/DivyamJani}\textbullet \ +91 9712731286
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{CHARUSAT University} \hfill Changa, Gujarat

Degree, Concentration. CGPA : 7.5 [Till 3rd Sem] \hfill Expected March, 2026

B.Tech in Information Technology

\vspace{12pt}

\textbf{Nalanda Vidhyalaya} \hfill	Morbi, Gujarat

Percentage : 75\%
\hfill June, 2022 

\vspace{12pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Team Elementals} \hfill (Remote)

\textbf{Trainee Intern} \hfill May 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
   \item Discovered modern approaches to creating professional resumes, utilizing online tools and templates for a polished and standout presentation.
    \item Explored framework like Bootstrap.
    \item Passionate about crafting visually appealing and user-friendly interfaces using HTML and CSS, focusing on the design and functionality of the frontend part of websites.
\end{itemize}

\vspace{12pt}



\begin{center}
    \textbf{Projects }
\end{center}





\textbf{Seat Reservation System for Restaurants}	\hfill CSPIT, Changa, Gujarat

\textbf{Software Group Project} \hfill 4th Sem
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed a web-based application allowing users to book tables at various restaurants listed on the platform.
    \item Implemented advanced search and filter functionality to help users find restaurants based on location, and availability.
    \item Integrated functionality for efficient reservation processes, streamlining user interaction.

\end{itemize}

\vspace{12pt}


\begin{center}
    \textbf{Leadership \& Activities}
\end{center}

\textbf{Spoural , Charusat}	\hfill Changa, Gujarat
\newline
\textbf{Rotaract Club , Charusat}	\hfill Changa, Gujarat

\textbf{Member} \hfill July 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
   \item Focuses on the development of young adults as leaders in their communities and workplaces.
   \item Formal meetings were held in person or virtually, usually every two weeks, which feature speakers, special outings, social activities, discussions or visits to other clubs.

\end{itemize}


% trying


\vspace{12pt}

\begin{center}
    \textbf{Skills \& Interests }
\end{center}

\textbf{Technical:} C, C++, HTML, CSS, JS.

\textbf{Language:} English, Hindi ,Gujarati 

\textbf{Sports:} Volleyball, Badminton, Swimming, Basketball.

\textbf{Interests:} Passionate about listening to Bollywood songs, Active participant in sports, particularly enjoys playing badminton and volleyball, Playing Video games.




\end{document}
